Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-12 krs-survey.tex
Introduction section Representation

@@

Thematic roles

Spatio-Temporal Representations:

@@

\subsubsection{Design Strategy}

>>>>

We do not discuss in this section the general strategies to construct a
knowledge model (they will be presented in
section~\ref{sect|design-strategies}). We focus here on questions that involve
representational challenges (time, space, context) or require specific
cognitive capabilities (theory of mind, introspection, memory).

@@

This section discusses strategies and approaches to represent in a knowledge
model three important \emph{roles}\fxwarning{Reference on the term 'role'?}.

@@

\subsubsection{Design Strategy}
\label{sect|design-strategies}
